---
title: "Machine Learning in R"
site: distill::distill_website
---

Efficient, object-oriented programming on the building blocks of machine learning.

<div class="grid-container">
  <div class="grid-item">
  <div class="grid-icon"><i class="bi-alarm icon"></i></div>
  Easy interface for scientists and commercial applications.
  </div>
  <div class="grid-item">
  <div class="grid-icon"><i class="bi-pen icon"></i></div>
  More than 100 machine learning algorithms.
  </div>
  <div class="grid-item">
  <div class="grid-icon"><i class="bi-github icon"></i></div>
  Clean OO-design with `R6` classes.
  </div>
  <div class="grid-item">
  <div class="grid-icon"><i class="bi-server icon"></i></div>
  Easy parallelization with the `future` package.
  </div>
  <div class="grid-item">
  <div class="grid-icon"><i class="bi-tsunami icon"></i></div>
  State-of-the-art optimization algorithms.
  </div>
  <div class="grid-item">
  <div class="grid-icon"><i class="bi-toggles icon"></i></div>
  Dataflow programming with pipelines.</div>
</div> 

<div class="btn-container">
<a href="github.com" class="btn"><i class="bi-github btn-icon"></i> GitHub</a>
<a href="github.com" class="btn"><i class="bi-book btn-icon"></i> Resources</a>
<a href="github.com" class="btn"><i class="bi-truck btn-icon"></i> Gallery</a>
<a href="github.com" class="btn"><i class="bi-twitter btn-icon"></i> Twitter</a>
</div>

# Code Example

## Basic

```{r, include=FALSE}
set.seed(7832)
lgr::get_logger("mlr3")$set_threshold("warn")
lgr::get_logger("bbotk")$set_threshold("warn")
```

```{r, eval=FALSE}
library(mlr3)

# retrieve task
task = tsk("penguins")

# load learner and set hyperparameter
learner = lrn("classif.rpart", cp = .01)

# automatic resampling
resampling = rsmp("cv", folds = 3L)
rr = resample(task, learner, resampling)

# set measure and score
measure = msr("classif.acc")
rr$score(measure)
```

## Tuning

```{r, eval=FALSE}
library(mlr3tuning)
library(mlr3tuningspaces)

# retrieve task
task = tsk("penguins")

# load learner and set search space
learner = lts(lrn("classif.rpart"))

# hyperparameter tuning on the penguins data set
instance = tune(
  method = "random_search",
  task = task,
  learner = learner,
  resampling = rsmp("cv", folds = 3),
  measure = msr("classif.acc"),
  term_evals = 10,
  batch_size = 5
)

# best performing hyperparameter configuration
instance$result
```

## Pipelines

```{r, eval=FALSE}
library(mlr3)
library(mlr3pipelines)
library(mlr3learners)

# retrieve task
task = tsk("german_credit")

# set base and super learner
base_learners = list(
  lrn("classif.rpart", predict_type = "prob"),
  lrn("classif.kknn", predict_type = "prob")
)
super_learner = lrn("classif.log_reg")

# create pipeline and convert to graph learner
graph_stack = pipeline_stacking(base_learners, super_learner)
graph_learner = as_learner(graph_stack)

# train on german credit task
graph_learner$train(task)
```

